Mining of Keystroke and Mouse Dynamics to Increase the Engagement of Students with Programming Assignments

### 2018-04-21 paper.tex
Changes

An experiment was conducted where students solved a series of programming
assignments using the web based learning environment. Using only the
data from the student\'s keyboard and mouse dynamics six affective
states where recognized for each of the attempts at solving the
assignments. Results obtained from the experiment are promising. The
affective states recognized include the most common in novice
programmers according to the study of Bosch, D'Mello \& Mills
\cite{bixler2013detecting}: boredom, engagement/flow, confusion and
frustration. For the initial experiment \cite{ijcci17}

four binary classifiers were compared: J-48 decision trees, k-nearest neighbour
classifier, feed forward neural network, and a na\"ive Bayes. The output of each
classifier determined if the student experienced the affective state during the
assignment. In this experiment we will also use 
Deep Learning \cite{candel2016deep} and  Gradient Boosted Trees 
via H2O version 3.8.2.6, and the Random Forest and Na\"ive Bayes Kernel 
implementatios from RapidMiner Studio version 8.1.

>>>>

An experiment was conducted where students solved a series of programming
assignments using the web based learning environment. Using only the
data from the student\'s keyboard and mouse dynamics six affective
states where recognized for each of the attempts at solving the
assignments. Results obtained from the experiment are promising. The
affective states recognized include the most common in novice
programmers according to the study of Bosch, D'Mello \& Mills
\cite{bixler2013detecting}: boredom, engagement/flow, confusion and
frustration. For the initial experiment \cite{ijcci17} 
four binary classifiers were compared: J-48 decision trees, k-nearest neighbour
classifier, feed forward neural network, and a na\"ive Bayes. The output of each
classifier determined if the student experienced the affective state during the
assignment. In this experiment we will also use 
Deep Learning \cite{candel2016deep} and  Gradient Boosted Trees 
via H2O version 3.8.2.6, and the Random Forest and Na\"ive Bayes Kernel 
implementatios from RapidMiner Studio version 8.1.
